\textbf{ Accurate spectrophotometric estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-07-31 paper/sp.tex
much of the results section

HOGG: We do 2-fold train-and-test to make results independent of \gaia.

We compute our precision how? Figures.

We set the regularization parameters how? And why?

>>>>

We optimize two models, one for Training Set A and one for Training Set B.
For optimization, we use \code{scipy} l-bfgs-b (HOGG CHECK), starting at
an uninformed starting point in the $\theta$ space.
The optimization is of the objective function given in (HOGG WHAT EQUATION) above,
and although this optimization is not convex, it appears to converge to the
same good solution quickly and reliably from multiple different starting points.

The two models are applied to the two splits of the Parent Sample, Parent Sample
A and Parent Sample B, using the A-trained model on Parent Sample B and
\foreign{vice versa}.
For the purposes of assessing the accuracy and precision of the model, this
train-and-test framework constitutes a two-fold cross-validation.
Results of this cross-validation is shown in HOGG WHAT FIGURE.
For the stars with highest \gaia-measured parallax signal-to-noise,
the spectrophotometric model is predicting the \gaia\ parallaxes with little bias
and a scatter of better than 9~percent.

We used this cross-validation framework to adjust the regularization parameters.
We (arbitrarily) chose zero regularization on the photometric components of the
$x_n$ vectors, and uniform, identical regularization strength for all of the
spectral (\apogee-pixel) components.
We did a coarse grid search in the value for the spectral-component value of the
$\lambda$ vector, using the A/B split as the two-fold cross-validation.
The 9-percent scatter is what we obtain at the optimal setting of the regularization
strength.

We adopt 9~percent as the method's precision.
This estimate is conservative in that the 9-percent scatter includes contributions
from both our spectrophotometric model and from the \gaia\ measurements themselves.
However this estimate is not so conservative in that the test is performed with
\gaia's best stars, which are bright, nearby, in low extinction regions, and
(because of these things) near Solar metallicity.
There could in principle be additional bias or scatter for stars that are in dustier
regions or at lower metallicities.
\figurename~HOGG WHAT FIGURE shows that
there is no suggestion of any such trends when we color the residuals by metallicity
or $H-W_2$ (which is a reddening proxy).

HOGG: validation with clusters and Sag.
